Lessons Learned for JWST Transiting Planet Time Series from Ground-based Studies of the NIRCam Detectors

### 2019-05-14 ms.tex
fixed the zoomed-in row-by-row subtraction

\subsection{Long Darks}\label{sec:longDarks}

@@

\textcolor{blue}{New Change to do it properly: We return to the reduced slope file that has reference pixels subtracted and the bias subtracted.
Here we subtract the median value from each row in each group.
Doing the subtractions for each group gave an RMS that was 50 ppm smaller for aperture 0, 80 ppm larger for aperture 1 and 31 ppm smaller for aperture 3.}
In the latter case, the standard deviation of the time series drops to 6000 DN, but is still larger than the expectation of 1310 DN of all noise were uncorrelated.
The A3 detector used for weak lens photometry has reduced 1/f noise.
The standard deviation of the raw time series is 15,000 compared with the 22,000 from the A5 (ALONG) detector.

@@

\begin{figure*}[!hbtp]
\centering
\includegraphics[width=.37\columnwidth]{ap_labels_darkRedRowColSub_NRCALONG-DARK-7235074213_1.pdf}
\includegraphics[width=.37\columnwidth]{ap_labels_darkRedsmoothedRowKernel_NRCALONG-DARK-7235074213_1.pdf}
\includegraphics[width=.37\columnwidth]{zoom_long_dark_darkRedRowColSub}
\includegraphics[width=.37\columnwidth]{zoom_long_dark_darkRedsmoothedRowKernel.pdf}
\caption{The same apertures as Figure \ref{fig:longDarkPhot}, but with subtraction by a smoothed image along the rows.
Subtraction by the smoothed image has a dramatic effect on reducing correlated 1/f read noise.
}\label{fig:longDarkWithRowKernel}
\end{figure*}

>>>>

\clearpage
\subsection{Long Darks}\label{sec:longDarks}

@@

In the latter case, the standard deviation of the time series drops to 6000 DN, but is still larger than the expectation of 1310 DN of all noise were uncorrelated.
The A3 detector used for weak lens photometry has reduced 1/f noise.
The standard deviation of the raw time series is 15,000 compared with the 22,000 from the A5 (ALONG) detector.

@@

\begin{figure*}[!hbtp]
\centering
\includegraphics[width=.37\columnwidth]{ap_labels_row_by_row_group_sub_aps_1_NRCALONG-DARK-7235074213_1}
\includegraphics[width=.37\columnwidth]{ap_labels_darkRedsmoothedRowKernel_NRCALONG-DARK-7235074213_1.pdf}
\includegraphics[width=.37\columnwidth]{zoom_long_dark_row_by_row_group_sub.pdf}
\includegraphics[width=.37\columnwidth]{zoom_long_dark_darkRedsmoothedRowKernel.pdf}
\caption{The same apertures as Figure \ref{fig:longDarkPhot}, but with subtraction by a smoothed image where a 40 pixel wide and 1 pixel tall averaging kernel was applied along the fast read direction of every group.
Subtraction by the smoothed image has a dramatic effect on reducing correlated 1/f read noise from $\sim$6,000 DN to $\sim$700 DN in the aperture.
}\label{fig:longDarkWithRowKernel}
\end{figure*}
\clearpage
